\problem{18}
\subsection*{Part \textbf{a.}}
As hinted in the problem, we use Theorem 5.8a. in the textbook to find a linear functional $f\from \vesp \to \CC$ such that $\v f\v=1$, $f(\MM)=0$, and $f(x)=\delta>0$.

Next we show (it's probably unnecessary) that when $x\notin \MM$ then the $\MM + \CC x$ is a direct sum, namely: $\MM \oplus \CC x$. 
Showing that $\MM\cap \CC x$ is simple: take $m+zx\in \MM \cap \CC x$, then, 
$$f(m+zx)=z\delta =0$$
Thus $z=0$. Note that here need to use that $\delta>0$.

Now, take two elements that happen to add up to the same vector:
$$m+zx = m'+z' x$$
where $m,m' \in \MM$ and $z,z'\in \CC$. 
Evaluating $f$ on both sides cancels the $\MM$ component and all that is left is $z=z'$. 
This implies that $m=m'$.

To prove that $\MM+\CC x$ is closed as a subspace of $\vesp$; we will take any one of its limit points and show it is inside the subspace.
Take $\alpha \in \vesp$ such that it is a limit point of $\MM+\CC x$.
Then we have a sequence $\{\alpha_n \}\subset \MM+\CC x$ such that $\alpha_n \to \alpha$.
Since $\v f\v=1$ and thus continuous:
$$f(\alpha) = \lim_{n\to \infty} f(\alpha_n)= \lim_{n\to \infty} z_n \delta = z\delta$$
Every $\alpha_n = m_n = z_n x$, where the components are unique, by the direct sum result above. 
Then $\alpha_n - z_n x$ tends to some vector that we call $m$. 
All that is left is to show $m\in \MM$; this is easy as $f(\alpha_n - z_n x) =0$ for all $n$.

\subsection*{Part \textbf{b.}}
We start with the base case $\MM_0 =\{0\}$, which is closed as all points are in a Haussdorff space.
By the result in part (a): for any $n$ such that $\MM_n$ is $n$-dimensional and closed; if there is an $x$ such that:
$$\delta=\inf_{y\in \MM_n}\v x+y\v>0$$
then we can make the \emph{closed} $(n+1)$-dimensional subspace $\MM_{n+1}=\MM_n + \CC x$. 
And for the finite dimensional case we can always find such an $x$ just taking any unused element in the basis.

\problem{19}
\subsection*{Part \textbf{a.}}
Take $x_0=0 $ and define $\MM_0= \{0\}$ which is a closed subspace of $\vesp$.
For any $n\in \NN$, assume that $\MM_{n} $ is a closed subspace; then taking $\epsilon = 1/2$, we already know there
exists $x_{n+1}\in \vesp$ such that:
$$\v x_{n+1}\v = 1 \text{ and } \v x_{n+1} + \MM_n \v \geq 1-1/2$$
and to keep up with the inductive definition, we also set $\MM_{n+1} = \MM_n+\CC x_{n+1}$.

The process above produce the desired sequence because: 1) All $x_n$ are taken from the $\vesp$'s unit ball.
And, 2) for any $x_j,x_k$ assume $j>k$; then, $x_k \in \MM_k$ by definition, and $\MM_k\subset \MM_j$ thus:
$$\v x_j - x_k\v\geq \inf_{y\in \MM_{k}}\v x_j -y \v \geq \inf_{y\in \MM_{j-1}} \v x_j -y\v \geq 1/2$$

\subsection*{Part \textbf{b.}}
We argue by contradiction:
Suppose $\vesp$ is locally compact and infinite dimensional. 
Then, by the definition of a locally compact space we know that there is compact set $K$ that contain an open ball around the origin of radius $\epsilon>0$, namely:
$$0\in B_0(\epsilon) \subset K$$
If we now take the sequence contructed above and scale it to the $\epsilon$-radius ball, then $\{\epsilon x_j \}$ are a sequence contained inside $K$ that have no converging subsequences (no two elements ever get closer than $\frac 12 \epsilon$).
Thus contradicting that $K$ is compact. 

\problem{22}
\subsection*{Part \textbf{a.}}
First, to check that $T^\dagger$ is linear take $\alpha, \beta$ scalars and $f,g\in \vespy$ we have:
$$T^\dagger (\alpha f+\beta g)= (\alpha f+ \beta g) \circ T = \alpha T^\dagger f + \beta T^\dagger g $$
To check that $T^\dagger $ is bounded, first we have:
$$\v T^\dagger f \v = \v f\circ T \v \leq \v f\v \v T\v $$
Thus $\v T^\dagger \v \leq \v T\v$. On the other hand:
$$\v T^\dagger \v  = \sup_{\v f\v =1} \v T^\dagger f \v$$
Since $T^\dagger f$ is an element of $\vesp^*$ it has the dual norm:
$$\v T^\dagger \v  = \sup_{\v f\v =1} \left\{ \sup_{\v x\v =1} \v (T^\dagger f)x\v \right\}$$
For every $Tx\neq 0$ by the Hahn-Banach Theorem, we know there exists $\v f_0 \v =1$ such that $f_0(Tx) = \v T x\v$. Then relaxing the first supremum above:
$$\geq \sup_{\v x\v =1} \v f_0\v \v Tx\v =\sup_{\v x\v =1} \v Tx\v = \v T \v$$
\subsection*{Part \textbf{b.}}
First, let us assume that $T\vesp$ is dense in $\vespy$. Take any two $f,f'\in \vespy^*$ such that:
$$T^\dagger f = T^\dagger f'$$
Then, for all $x\in \vesp$ we have:
$$(fT)x= (f'T)x$$
Since the range of $T$ is dense, for all $y\in\vespy$ there exists $\{x_n\}$ such that $Tx_n \to y$. Thus, using the continuity of the elements in $\vespy^*$,
$$ fTx_n \to fy = f'y \leftarrow f'Tx_n$$
Note that $y$ was chosen arbitrarily, this means that $f=f'$, which implies that $T^\dagger $ is one-to-one.

Conversely, suppose that $T^\dagger $ is injective. This implies that for $f\neq 0$ we must have $T^\dagger f\neq 0$. This last non-equality implies there exists $x\in\vesp$ such that $f(Tx)\neq 0$ and thus $Tx\neq 0$. Without loss of generality we may assume $Tx=1$. What is important is that now we can show that the range of $T$ is dense around $0\in \vespy$ since we can take the sequence $\{Tx/n\}$ for all $n\in \NN$. For an arbitrary point  $y \in \vespy$ and some point $Tx\neq y$; translate to $0$ and $Tx-y$ respectively. With this we are in the same situation as before, since, there exists $y^*\in \vespy^*$ such that:
$$y^*(Tx-y) = \delta>0$$
As before, this implies $T^\dagger y^*\neq 0$ and there exists $x_1\in \vesp$ such that 
$$(T^\dagger y^*)x_1 =1$$
Which gives the desired result.
